Ferromagnetism and spin excitations in topological Hubbard models with a flatband

### 2018-12-24 paper/paper.tex
Revised manuscript for PRB.

\par We would like to remark that the downward renormalization of the energies of the collective modes affected by the boundary bottoms of the Stoner continuum shares similarity with that observed in the two-dimensional antiferromagents, where the spin waves are interpreted as bound states of confined spinons and the suppression of energies of spin waves around the continuum bottom is attributed to their couplings to the nearby deconfined spinon continuum\cite{ZFSMC_PRL2006,TS_PRL2013,DMCNTPEMIR_NP2015,SQCCMS_PRX2017,YWDYL_PRB2018}. In addition, although correlated nearly-flat topological bands are hard to realize in real materials, they are possible to be designed in cold-atom systems. In fact great progress has been made very recently \cite{LCJPS_N2009,AALBPB_PRL2013,MSKBK_PRL2013,JMDLUGE_N2014}. We expect our results will stimulate related investigations in future cold-atom experiments.

>>>>

\par We would like to remark that the downward renormalization of the energies of the collective modes affected by the boundary bottoms of the Stoner continuum shares similarity with that observed in the two-dimensional antiferromagents, where the spin waves are interpreted as bound states of confined spinons and the suppression of energies of spin waves around the continuum bottom is attributed to their couplings to the nearby deconfined spinon continuum\cite{ZFSMC_PRL2006,TS_PRL2013,DMCNTPEMIR_NP2015,SQCCMS_PRX2017,YWDYL_PRB2018}. Intriguing flatband physics arises not only in models with repulsive interactions, but also in those with attractive ones\cite{PT_NC2015,JPVKT_PRL2016,LVPSHT_PRB2017,TLP_arXiv2018}, where the Bardeen-Cooper-Schrieffer superconducting state is the exact ground state in the flatband limit\cite{PT_NC2015,JPVKT_PRL2016}. We hope our methods can be generalized to these systems beyond the flatband limit. In addition, although correlated nearly-flat topological bands are hard to realize in real materials, they are possible to be designed in cold-atom systems. In fact great progress has been made very recently \cite{LCJPS_N2009,AALBPB_PRL2013,MSKBK_PRL2013,JMDLUGE_N2014}. We expect our results will stimulate related investigations in future cold-atom experiments.
